Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-10 Paper/ms.tex
periods figure

@@

>>>>

The posterior distribution for the logarithms of the periods is shown in
Figure~\ref{fig:nu_oph_periods}. Because of the label-switching degeneracy,
the posterior samples for all periods were combined to make this figure, which
shows three prominent peaks. Defining the log-periods by
$S_i =  \log_{10}(T/\textnormal{1 day})$,
Figure~\ref{fig:nu_oph_periods} is a Monte Carlo representation
of the mixture distribution
\begin{eqnarray}
f(S) &=& \sum_{N=1}^{10} \frac{1}{N}\sum_{i=1}^N p(S_i | N, \boldsymbol{D}).
\end{eqnarray}

@@

\begin{figure}
\includegraphics[scale=0.5]{Figures/nu_oph_periods.eps}
\caption{The posterior distribution for the orbital periods in the $\nu$ Oph
system.\label{fig:nu_oph_periods}}
\end{figure}
